---
categories:
- ""
- ""
date: "2017-10-31T22:42:51-05:00"
description: 
draft: false
keywords: ""
slug: magna
title: Drink Consumption
---

```{r, setup}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,
  size="small")
options(digits = 3)

knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(mosaic)
library(ggthemes)
library(lubridate)
library(fivethirtyeight)
library(here)
library(skimr)
library(janitor)
library(vroom)
library(tidyquant)
library(rvest)
```

# Where Do People Drink The Most Beer, Wine And Spirits?

Back in 2014,
[fivethiryeight.com](https://fivethirtyeight.com/features/dear-mona-followup-where-do-people-drink-the-most-beer-wine-and-spirits/)
published an article on alchohol consumption in different countries. The
data `drinks` is available as part of the `fivethirtyeight` package.
Make sure you have installed the `fivethirtyeight` package before
proceeding.

```{r, load_alcohol_data}
library(fivethirtyeight)
data(drinks)
```

What are the variable types? Any missing values we should worry about?

There is 1 character variable and 4 numeric variables. No missing
values to worry about.

```{r glimpse_skim_data}
drinks %>% skim #Skim the data for variable types and missing values.
```

There is 1 character variable and 4 numeric variables. No missing values to worry about.


Make a plot that shows the top 25 beer consuming countries

```{r beer_plot}
#Create a plot to show the top 25 beer consuming countries
drinks %>%
  slice_max(order_by=beer_servings, n=25) %>%  #Select the top 25 beer consuming countries data
  ggplot(aes(x=beer_servings, y=reorder(country,beer_servings))) + # Plot the data, descending order
  geom_col() +
  theme_bw() +
  labs(title='Beer Consumption by Country', subtitle= 'Top 25', x='Servings (per person)', y='Country') + 
  NULL
```

Make a plot that shows the top 25 wine consuming countries

```{r wine_plot}
#Create a plot to show the top 25 wine consuming countries
drinks %>%
  slice_max(order_by=wine_servings, n=25) %>% #Select the top 25 wine consuming countries
  ggplot(aes(x=wine_servings, y=reorder(country, wine_servings)))+ # Plot the data, descending order
  geom_col() +
  theme_bw() +
  labs(title='Wine Consumption by Country',subtitle= 'Top 25', x='Servings (per person)', y='Country') + 
  NULL
```

Finally, make a plot that shows the top 25 spirit consuming countries

```{r spirit_plot}
#Create a plot to show the top 25 spirit consuming countries
drinks %>%
  slice_max(order_by=spirit_servings, n=25) %>% #Select the top 25 spirit consuming countries
  ggplot(aes(x=spirit_servings, y=reorder(country,spirit_servings))) + # Plot the data, descending order
  geom_col() +
  theme_bw() +
  labs(title='Spirit Consumption by Country', subtitle= 'Top 25', x='Servings (per person)', y='Country') + 
  NULL
```

What can you infer from these plots? Don't just explain what's in the
graph, but speculate or tell a short story (1-2 paragraphs max).

> TYPE YOUR ANSWER AFTER (AND OUTSIDE!) THIS BLOCKQUOTE.

Rudimental factors that affect consumption of beer, wine, and spirit
include production levels, drinking age limit, pricing, and culture.

Based on the data, it can be observed that beer consumption is the
highest for Namibia, Czech Republic, Gabon, and Germany. This can
perhaps be attributed to the beer triangle in Namibia, low-cost beer in
Czech Republic (cheaper than water), and the lowest drinking age in
Germany (16 as opposed to 18 for other countries) (Kohli 2021, Nugent
2021) .

As for wine consumption, France (370 wine servings), Portugal, Andorra,
and Switzerland top the list while Ireland is in position 25, at 150
servings. The distribution of the 25 countries seems to have high
variance.

Lastly, similar to the wine consumption distribution, spirit consumption
also appears to have high variance. While Grenada has a high consumption
of spirits perhaps due to culture (women have higher per capita
consumption than men) and Belarus due to the relaxed policies, Mongolia
may have lower consumption as they prefer their regional fermented milk
alcohol drinks (OECD 2020).
